Price of Anarchy for Mean Field Games

### 2018-07-26 PoA.tex
sketch of Prop 7 Case 4

@@

	If 
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}
	\end{equation*}
	then 
	$$ \lim_{b_2 \to \infty} PoA = 1,$$	
	otherwise, 
	$$ \lim_{b_2 \to \infty} PoA >1.$$
\label{prop:b2_to_infty}
\end{proposition}

@@

	% upper bound for u_t, w_t
	Also, from equation (\ref{eq:riccati_ut_sol}), for any fixed $b_2$, we can compute the derivative of $u_t^{b_2}$ with respect to time $t$:
	\begin{equation*}
		\frac{d u_t^{b_2}}{dt} = \frac{\left(B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \right) \cdot \left(\delta_u^{+,b_2} - \delta_u^{-,b_2}\right)^2 e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t) } }{\left[B^{b_2} D^{u,b_2}(1-e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)})   + \delta_u^{+,b_2}e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)}- \delta_u^{-,b_2}  \right]^2 }.
	\end{equation*}
	Hence, the function $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
	$$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$$
	there exists $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ is increasing and 
	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} = \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$
	Thus,
	\begin{equation*}
	\left\vert u_t^{b_2}\right\vert \leq D^{u,b_2 \to \infty} + 1 , \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,u,upper},
	\label{eq:u_t_bound}
	\end{equation*}
	and by the same argument for $w_t^{b_2}$ and $\eta_t^{b_2}$, there exists $b_2^{*,upper} \geq b_2^{*,u,upper}$ such that
	%for all $t \in [0,T]$ and $b_2 \geq b_2^{*,w,upper}$,
	%\begin{equation*}	
	%$\left| w_t^{b_2}\right|\leq D^{w}.$
	%\label{eq:w_t_bound}
	%\end{equation*}

@@

	Todo: case $b_1 \to \infty$ and $\bar{b}_1 \to \infty$.
\end{proof}

>>>>

It will also be useful to compute the derivative of $u_t$ with respect to time $t$ from the explicit form in equation (\ref{eq:riccati_ut_sol}):
\begin{equation}
\frac{d u_t}{dt} = \frac{\left(B (D^{u})^2 + 2 A^u D^{u} - C^{u} \right) \cdot \left(\delta_u^{+} - \delta_u^{-}\right)^2 e^{- (\delta_u^{+} - \delta_u^{-})(T-t) } }{\left[B D^{u}(1-e^{- (\delta_u^{+} - \delta_u^{-})(T-t)})   + \delta_u^{+}e^{- (\delta_u^{+} - \delta_u^{-})(T-t)}- \delta_u^{-}  \right]^2 }.
\label{eq:riccati_ut_sol_deriv}
\end{equation}
Note that $u_t$ is increasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}>0$, and likewise, decreasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}<0$.

@@

	If 
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	then 
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
	Otherwise, 
	$$ \lim_{b_2 \to \infty} PoA >1.$$
\label{prop:b2_to_infty}
\end{proposition}

@@

	% upper bound for u_t, w_t
	From equation (\ref{eq:riccati_ut_sol_deriv}), we see that $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
	$$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$$
	there exists $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ is increasing and 
	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} = \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$
	Thus,
	\begin{equation*}
	\left\vert u_t^{b_2}\right\vert \leq D^{u,b_2 \to \infty} + 1 , \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,u,upper},
	\label{eq:u_t_bound}
	\end{equation*}
	and by the same argument for $w_t^{b_2}$ and $\eta_t^{b_2}$, there exists $b_2^{*,upper} \geq b_2^{*,u,upper}$ such that
	%for all $t \in [0,T]$ and $b_2 \geq b_2^{*,w,upper}$,
	%\begin{equation*}	
	%$\left| w_t^{b_2}\right|\leq D^{w}.$
	%\label{eq:w_t_bound}
	%\end{equation*}

@@

	Todo: case $b_1 \to \infty$ and $\bar{b}_1 \to \infty$.

	Now, consider $\bar{b}_1 \to \infty$.
	Since $\lim_{\bar{b}_1 \to \infty} |A^{u,\bar{b}_1}|=\infty$, we have:
	\begin{equation*}
	\begin{split}
	\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u&=2 \sqrt{(A^{u,\bar{b}_1})^2+BC^u} \\
	&\xrightarrow[\bar{b}_1 \to \infty]{}\infty,
	\end{split}
	\end{equation*}
	and
	\begin{equation*}
	\begin{split}
	-\delta^{-,\bar{b}_1}_u&=A^{u,\bar{b}_1}+\sqrt{(A^{u,\bar{b}_1})^2+BC^u} \\
	&\xrightarrow[\bar{b}_1 \to \infty]{}0.
	\end{split}
	\end{equation*}
	Therefore, it can be shown that for $t \in [0,T)$:
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\frac{u^{\bar{b}_1}_t}{\bar{b}_1}=\frac{1}{B}.
	\end{equation*}
	Similarly, for $t \in [0,T)$:
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\frac{w^{\bar{b}_1}_t}{\bar{b}_1}=\frac{2}{B}.
	\end{equation*}
	Thus,
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty} \left(\frac{u^{\bar{b}_1}_t}{\bar{b}_1}-\frac{w^{\bar{b}_1}_t}{\bar{b}_1}\right)^2=\frac{1}{B^2}.
	\end{equation*}

	Note that $\eta_t$, and therefore $v_t$, are independent of $\bar{b}_1$. Thus,
	\begin{equation*}
	\begin{split}
	\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}&=\frac{1}{2\bar{b}_1^2}\left[\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T\right] + \frac{w^{\bar{b}_1}_0}{2\bar{b}_1^2} (\mathbb{E}(\xi))^2\\
	&\xrightarrow[\bar{b}_1 \to \infty]{}0.
	\end{split}
	\end{equation*}

	Now, consider:
	\begin{equation*}
	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{B}{2}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}} \left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 e^{2\int_0^t (b_1+\bar{b}_1-B u_s^{\bar{b}_1})ds} dt.
	\end{equation*}
	(ToDo: Show $\frac{u^{\bar{b}_1}_t}{\bar{b}_1} \to \frac{1}{B}$ and $\frac{w^{\bar{b}_1}_t}{\bar{b}_1} \to \frac{2}{B}$ UNIFORMLY for $t \in [0,T/2]$. OR show both are uniformly bounded and use the bounded convergence theorem.)

	Then for $\zeta:=\frac{1}{B^2}$, there exists $\bar{b}_1^{*,u,w}$ such that for $t\in[0,T/2]$ and $\bar{b}_1 \geq \bar{b}_1^{*,u,w}$,
	\begin{equation*}
	\left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 \geq \frac{1}{B^2}-\zeta=\frac{1}{2B^2}.
	\end{equation*}
	Then,
	\begin{equation*}
	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{1}{4B}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}}e^{2\int_0^t (b_1+\bar{b}_1-B u_s^{\bar{b}_1})ds} dt.
	\end{equation*}

	Since $\lim_{\bar{b}_1 \to \infty}B (D^{u})^2 + 2 A^{u,\bar{b}_1} D^{u} - C^{u}=-\infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) there exists a $\bar{b}_1^{*,dec}$ such that for $\bar{b}_1 \geq \bar{b}_1^{*,dec}$, $t \mapsto u_t^{\bar{b}_1}$ is decreasing, and thus, $(\bar{b}_1-B u_t^{\bar{b}_1})\geq (\bar{b}_1-B u_{0}^{\bar{b}_1})$.

	(ToDo: Show $(\bar{b}_1-B u_0^{\bar{b}_1}) \to 0$.)

	Let $\zeta_2>0$. Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) = 0$, there exists $\bar{b}_1^{*} \geq \max \{\bar{b}_1^{*,u,w},\bar{b}_1^{*,dec} \}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$,
	\begin{equation*}
	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{1}{4B}(\mathbb{E}(\xi))^2 \int_0^{\frac{T}{2}}e^{2tb_1}e^{-2t\zeta_2}dt=:c_{\Delta SC}>0,
	\end{equation*}
	and therefore:
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}>0.
	\end{equation*}
	Thus, we conclude:
	\begin{equation*}
	\begin{split}
	\lim_{\bar{b}_1 \to \infty}\frac{\Delta SC^{\bar{b}_1}}{SC^{MKV,\bar{b}_1}}=\lim_{\bar{b}_1 \to \infty}\frac{\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}}{\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}}=\infty,
	\end{split}
	\end{equation*}
	and therefore,
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty} PoA^{\bar{b}_1}=\infty.
	\end{equation*}
